Detecting distributional differences between temporal granularities for exploratory time series analysis

### 2021-06-10 paper/main.Rmd
added acknowledgment and supplementary section

>>>>

# Acknowledgments {-}

The Australian authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research. Sayani Gupta was partially funded by [Data61 CSIRO](https://data61.csiro.au/) during her PhD. The Github repository,  [github.com/Sayani07/paper-hakear](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials. This article was created with R [@R-language], `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown].

# Supplementary Materials

**Data and scripts:** Data sets and R code to reproduce all figures in this article (main.R).

\noindent
**Simulation results and scripts:** All simulation table, graphics and and R code to reproduce it (paper-supplementary.pdf, paper-supplementary.Rmd)

\noindent
**R-package:** The open-source R [@R-language] package `hakear` [@R-hakear] is available on Github (https://github.com/Sayani07/hakear) to implement ideas presented in this paper.
